\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-08 main.tex
clean up bibbib

This functionality can be seen as a matching exercise
\citep{stuart2010matching, mcintosh2018using} in the spatio-temporal
domain to pair up nearby observations. It can also be considered as a
form of data fusion \citep{castanedo2013review, cocchi2019data}, where
data from multiple sources are combined together.

@@

Figure \ref{fig:interactive-popup} shows Figure
\ref{fig:interactive-linking} made made with leaflet and popups.

>>>>

This functionality can be seen as a matching exercise
\citep{stuart2010matching, mcintosh2018using} in the spatio-temporal
domain to pair up nearby observations. It can also be considered as a
form of data fusion \citep{cocchi2019data}, where data from multiple
sources are combined together.

@@

Figure \ref{fig:interactive-popup} shows Figure
\ref{fig:interactive-linking} made made with leaflet and popups
\citep{leafpop}.
